Aa Language Reference Manual

### 2011-12-26 v2/Ahir-asm/devel/docs/AaLRM.tex
Fixed the handling of undefined memory accesses..  If Aa2VC sees a memory access which "points nowhere", it will treat the result as undefined...  that is, the access will just be ignored.
Continual reorganization.  Also changed vc2vhdl so that the number of banks in a memory space defaults to 1 (overrides through attribute settings in the vc file only).
Some other observations: performance differences
between -a and no -a are minimal..  The preferred
default case should be -q -a for min area, max
rate.

\section{Program Variables}

@@

>>>>

\section{Program Variables} \label{sec:Objects}

@@

\section{Inline and Macro Modules}

By default, each distinct module in an \Aa program
is eventually implemented as a separate VHDL entity
by downstream AhirV2 tools (though downstream
tools are free to instantiate multiple
copies of this entity).

However, in order to give the \Aa programmer
more flexibility,  a module in \Aa may be marked
to be inlined or substituted into the program
at the point of the call.  The AhirV2 utility
{\bf AaOpt} is responsible for this substitution.

\subsection{Inlined Modules}

An inlined module is substituted into the
point of a call to it in a three-step manner.
The input arguments are sampled at the point
of the call, the body of
the module is invoked and the output arguments
are transferred.  The semantics of an inlined
function call are defined by this three step
procedure.  The input arguments are sampled
at the point of the call, and the output
arguments are updated at the termination of
the call.

For example, the following
program 
\begin{verbatim}
$inline $module [add] $in (a: $uint<32> b: $uint<32>)
    $out (c: $uint<32>) $is
{
    c := (a+b)
}

$module [add_check] $in (p: $uint<32> q: $uint<32>) 
    $out (r : $uint<32>) $is
{
    $call add (p q) (r)
}
\end{verbatim}
is translated to
\begin{verbatim}
$module [add_check]
$in ( p : $uint<32>   q : $uint<32>  )
$out ( r : $uint<32>  )
$is
{
  $seriesblock[add_18] 
  {
    $parallelblock[InArgs] 
    {
      add_18_a := p
      add_18_b := q
    }
    ( add_18_a => add_18_a add_18_b => add_18_b )
    $seriesblock[body] 
    {
      add_18_c := (add_18_a + add_18_b)
    }
    (  add_18_c => add_18_c )
    $parallelblock[OutArgs] 
    {
      r := add_18_c
    }
    ( r => r )
  }
  ( r => r )
}
\end{verbatim}
The three step substitution of add into add\_check
is clearly seen.

\subsection{Macro Modules}

A module defined as a macro (described below)
is directly substituted at the point of a call
to it.  That is, all references to input and
output arguments
are replaced by references to the corresponding
expression passed to the called function.  
The semantics are equivalent to a MACRO instantiation
in programming languages such as C/C++.

For example:
\begin{verbatim}
$macro $module [shift] $in (a: $uint<32>) 
    $out (c: $uint<32>) $is
{
    c := a 
}

$pipe inpipe: $uint<32>
$pipe midpipe: $uint<32>
$pipe outpipe: $uint<32>

$module [shift_check] $in () 
    $out () $is
{
    $call shift (inpipe) (midpipe)
    $call shift (midpipe) (outpipe)
}

\end{verbatim}
is equivalent to 
\begin{verbatim}
$pipe  inpipe : $uint<32>  $depth 1 
$pipe  midpipe : $uint<32>  $depth 1 
$pipe  outpipe : $uint<32>  $depth 1 
$module [shift_check]
$in ()
$out ()
$is
{
  $seriesblock[shift_14] 
  {
    midpipe := inpipe
  }
  $seriesblock[shift_17] 
  {
    outpipe := midpipe
  }
}
\end{verbatim}
The two calls to shift are replaced by
series blocks with input/output arguments
replaced by the expressions passed to them
at the point of the call.

Since it is possible to pass a pipe as an 
argument to a call, a macro-module is permitted
to violate the rule that there should
be at most one write to an interface object
within a module.
